### 2024-10-25 Paper/paperdraft_Sep2024.tex

    One may be concerned about potential differences in quality trends between clinical and non-clinical executive team hospitals leading to a violation in the parallel trends assumption. This is why I implement a synthetic difference-in-differences estimation strategy (\cite{arkhangelsky2021synthetic}). In particular, I weight more heavily any non-clinical team hospitals with pre-trends similar to clinical team hospitals in readmission, mortality, and baseline case mix. Further, I more heavily weight time periods that balance pre- and post-program outcomes for non-clinical teams. [description of weight distribution here]

@@

    The hypothesis driven from this theory is that clinically trained executives put more weight on quality of care before the financial incentives on quality began. To investigate this hypothesis empirically, I merge all general for-profit hospitals in the AHA data to the sample of nonprofit hospitals. Then, I compare readmission and mortality rates of always clinical executives and never clinical executives to for-profit hospitals after the incentive change. While I do not have information on leadership teams of for-profit hospitals, on average, they have revealed through their ownership status that they more heavily weigh profit. Thus, comparing different executive team behavior to for-profit behavior helps reveal how profit driven certain leadership teams are. Thus, I estimate the weighted synthetic difference-in-differences version of

@@

>>>>

    One may be concerned about potential differences in quality trends between clinical and non-clinical executive team hospitals leading to a violation in the parallel trends assumption. This is why I implement a synthetic difference-in-differences estimation strategy (\cite{arkhangelsky2021synthetic}). In particular, I weight more heavily any non-clinical team hospitals with pre-trends similar to clinical team hospitals in readmission, mortality, and baseline case mix. Further, I more heavily weight time periods that balance pre- and post-program outcomes for non-clinical teams. The control group consists of approximately 240 hospitals, and I show the fairly uniform distribution of their weights in Appendix \ref{app:sumstats}.

@@

    The hypothesis driven from the theory described in Section \ref{sec:forprofit} is that clinically trained executives put more weight on quality of care before the financial incentives on quality began. To investigate this hypothesis empirically, I merge all general for-profit hospitals in the AHA survey to my sample of nonprofit hospitals. Then, I compare readmission and mortality rates of always clinical executives and never clinical executives to for-profit hospitals after the incentive change. While I do not have information on leadership teams of for-profit hospitals, on average, they have revealed through their ownership status that they more heavily weigh profit. Thus, comparing different executive team behavior to for-profit behavior helps reveal how profit driven certain leadership teams are. Thus, I estimate the weighted synthetic difference-in-differences version of

@@

\begin{figure}
    \centering
    \caption{Control Group Weights, Readmission and Baseline Case Mix}
    \includegraphics[width=0.8\linewidth]{Objects/main_read_control_weights.pdf}
    \label{fig:main_read_control_weights}
\end{figure}

\begin{figure}
    \centering
    \caption{Time Weights, Readmission and Baseline Case Mix}
    \includegraphics[width=0.8\linewidth]{Objects/main_read_time_weights.pdf}
    \label{fig:main_read_time_weights}
\end{figure}

\begin{figure}
    \centering
    \caption{Control Group Weights, Mortality and Baseline Case Mix}
    \includegraphics[width=0.8\linewidth]{Objects/main_mort_control_weights.pdf}
    \label{fig:main_mort_control_weights}
\end{figure}

\begin{figure}
    \centering
    \caption{Time Weights, Mortality and Baseline Case Mix}
    \includegraphics[width=0.8\linewidth]{Objects/main_mort_time_weights.pdf}
    \label{fig:main_mort_time_weights}
\end{figure}
